
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Anuj Bhai Mehta}} & Email : \href{mailto:mehta.anuj2309@gmail.com}{mehta.anuj2309@gmail.com}\\
  \href{http://anujmehta.in/}{http://www.anujmehta.in} & Mobile : +91-94243 69410 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Shri Govindram Seksaria Institute of Technology and Science}{Indore, India}
      {Bachelor of Engineering in Computer Engineering;  GPA: 7.35/10 }{Aug. 2014 -- July. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Technical Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Manipulation and Recovery System}{CSE, SGSITS}
      {Asst. Prof Surendra Gupta}{Jan. 2016 - March 2016}
      \resumeItemListStart
        \resumeItem{}
          {Designed an algorithm to scale BMP images.}
        \resumeItem{}
          {Implemented Huffman’s algorithm for data compression and integrated above mentioned features in a web portal for easy accessibility.}  
        \resumeItem{}
          {Designed an algorithm to salvage inaccessible or lost images from secondary storage and removable media.}
      \resumeItemListEnd

    \resumeSubheading
      {Real Time News Geolocation Services}{MCA, SGSITS}
      {Asst. Prof Vandan Tewari}{Sep 2016 - Nov 2016}
      \resumeItemListStart
        \resumeItem{}
          {It is a location-aware news feed that provides a new platform for its users to get spatially related news updates from most reliable news sources.}
        \resumeItem{}
          {Google News and Orion are used to parse news feeds.}
      \resumeItemListEnd

    \resumeSubheading
      {Note Sharing and Management Application}{CSE,SGSITS}
      {Asst. Prof Preeti Khareop}{Sep 2016 - Nov 2016}
      \resumeItemListStart
        \resumeItem{Portfolio Management}
          {Designed a web portal (using singleton design pattern ) with group and real time multi-chat functionality along with media sharing and viewing facility.}
        \resumeItem{QuantDesk}
          {Provides users option to convert notes to pdf and share them with others in groups/contacts. The shared media can be viewed in note library and sharing history.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Animation and Simulation Modelling}{May 2017 - June 2017}
      {This project is available online at http://anujmehta.in}{}
      \resumeItemListStart
        \resumeItem{Travelling Salesman Problem}
          {}
        \resumeItem{Perlin Noise}
          {}
        \resumeItem{Warp Drive}
          {}
        \resumeItem{Genetic Algorithm}
          {}
        \resumeItem{}
          {Designed a particle system to simulate behavior of particles under influence of strong nuclear and gravitational forces.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Earthquake Visualizing System}{May 2017 - June 2017}
      {This project is available online at http://anujmehta.in}{}
      \resumeItemListStart
        \resumeItem{}
          {Designed a website to plot recent occurrences of earthquakes on a world map.}
        \resumeItem{}
          {Earthquake data was parsed from United States Geological Department’s Website.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Stock Trading Portal}{Nov 2016 - Dec 2016}
      {This project is available online at http://anujmehta.in}{}
      \resumeItemListStart
        \resumeItem{}
          {Designed a web portal to trade virtual stocks and shares.}
        \resumeItem{}
          {The actual prices of shares was parsed from live data at Yahoo Finance.}
        \resumeItem{}
          {Features of the portal include selling, buying, quoting stocks and viewing history of transactions. This portal was designed using MVC architecture.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{:C, C++, J2SE, Python (basic), JavaScript, Processing, SQL, PHP}
      \hfill
    }
    \item{
      \textbf{Software Worked on}{:WireShark, Argo UML, Octave, Netbeans, Codeblocks, MIT Scratch}
      \hfill
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
